\begingroup 
\renewcommand{\section}[2]{\anonsection{Библиографический список}}
\begin{thebibliography}{00}
\bibitem{1}
	T. Barabosch, A. Wichmann, F. Leder, and E. Gerhards-Padilla 
    Automatic extraction of domain name generation algorithms from current malware.//
    STO- MP-IST-111 Information Assurance and Cyber Defence, 2012.
\bibitem{2}
    P. Barthakur, M. Dahal, and M. K. Ghose.
    An efficient machine learning based classification scheme for detecting distributed command \& control traffic of p2p botnets.//
    5(10):9, 2013.
\bibitem{3}
    Click Security. Exercise to detect algorithmically generated domain names.//
    2014.
\bibitem{4}
    N. Davuth and S.-R. Kim.
    Classification of malicious domain names using support vector machine and bigram method.//
    7(1):51–58, January 2013.
\bibitem{5}
    J. Jacobs.
    Building a dga classifier.
    [Электронный ресурс] //
    URL: http://datadrivensecurity.info/blog/posts/2014/Oct/dga-part3/, October 2014
    (дата обращения:)
\bibitem{6}
    Raff.
    generation Dgas: A evolution.
    [Электронный ресурс] // 
    URL: http://www.seculert.com/blog/2014/11/dgas-a-domain-generation-evolution, November 2014.
    (дата обращения:)
\bibitem{7}
    M. Stevanovic and J. Pedersen.
    Machine learning for identifying botnet network traffic //, 2013.
\bibitem{8}
    Z. Wei-wei, G. Jian, and L. Qian.
    Detecting machine generated domain names based on morpheme features.//
    pages 408–411, october 2013.
\bibitem{9}
    9. S. Yadav, A. K. K. Reddy, A. L. N. Reddy, and S. Ranjan.
    Detecting algorithmically generated domain-flux attacks with dns traffic analysis.//
    20(5):1663–1677, Oct. 2012.
\bibitem{10}
    Н. О. Гончаров.
    Современные угрозы ботсетей.//
    10, октябрь 2014.
\bibitem{11}
    Machine Learning Text feature extraction (tf-idf)
    [Электронный ресурс] //
    URL: http://blog.christianperone.com/?p=1589
    (дата обращения:)
\bibitem{12}
    Understanding LSTM Networks
    [Электронный ресурс] //
    URL: http://colah.github.io/posts/2015-08-Understanding-LSTMs/
    (дата обращения:)
\bibitem{13}
    Chunting Zhou, Chonglin Sun, Zhiyuan Liu, Francis C.M. Lau
    A C-LSTM Neural Network for Text Classification //
    30 Nov 2015
\bibitem{14}
    Fidelis Threat Advisory #1016//
    Pushdo It To Me One More Time//
    16 Apr 2015
\end{thebibliography}
\endgroup

\clearpage
